### 2019-05-24 manuscript/introduction.tex

Polyploidy and self-fertilization are widely observed to be associated \citep{stebbins1950}.
There are several possible general explanations: whole genome duplication may facilitate the transition to selfing by masking inbreeding depression, self-fertilization may facilitate polyploidy establishment by avoiding the triploid bridge, or both selfing and polyploidy may be correlates of weedy or peripheral populations \citep{ramsey_1998, barringer2007, barrett2008, husband2008}.
% Boris, can you please check?  We need to be totally convincing about no SI-P.
Additionally, specifically in RNase-based gametophytic SI systems, polyploidization may directly cause the loss of SI \citep{stout1942, lewis1947}.
In these systems, self pollen fails because a pollen grain with one S-allele at the locus controlling the SI response is unable to detoxify the RNase produced by the same S-allele in the style. % ref?
The pollen of polyploids, however, has multiple S-alleles which act complementarily, detoxifying the RNases produced by any maternal genotype \citep{entani1999, tsukamoto2005, kubo2010}.
Polyploids are consequently capable of self-fertilization, with exceedingly few exceptions \citep{hauck_2002, nunes_2006}.
This system of RNase-based SI is regarded as ancestral in eudicots \citep{igic_2001,steinbachs_2002}, and it is expressed in all SI species of Solanaceae examined to date.
The consequent absence of SI polyploids in this family yields a strong correlation between ploidy and breeding system \citep{robertson_2011}.

>>>>

Polyploidy and self-fertilization are widely observed to be associated \citep{stebbins1950}.
There are several possible general explanations: whole genome duplication may facilitate the transition to selfing by masking inbreeding depression, self-fertilization may facilitate polyploidy establishment by avoiding the triploid bridge, or both selfing and polyploidy may be correlates of weedy or peripheral populations \citep{ramsey_1998, barringer2007, barrett2008, husband2008}.
Additionally, in RNase-based gametophytic SI systems, polyploidization alone directly causes the loss of SI \citep{stout1942, lewis1947}. %B: disclaimer: ceteris paribus statement omitted; polyploidization ordinarily causes SC because of the formation of heterodiploid pollen. On the background of deletion of S-locus, or with heterologous chromosome homozygosity at the S-locus may not do so. These, however, appear to be sufficiently rare that they are recovered perhaps twice in dicots: once (or twice) naturally, in sour cherry and it's close relative (Prunus), and once in a experimentally induced and selected synthetic pentaploid Solanum (which has not been replicated). Strictly speaking, this is a feature of non-self recognition systems of the kind found in RNase-based GSI.
In these systems, self-incompatibility is thought to occur because haploid self-pollen grains, with one S-allele at the locus controlling the SI response, are unable to detoxify the S-RNase produced by the same S-allele in the style \kubo{2010}. 
The unreduced pollen of tetraploids, however, can contain two S-alleles expressed in pollen, which jointly gain the ability to detoxify the S-RNases produced by any maternal genotype \citep{entani1999, tsukamoto2005, kubo2010}.
Polyploid individuals are consequently initially capable of self-fertilization, with exceedingly few exceptions \citep{hauck_2002, nunes_2006}.
This system of RNase-based SI is regarded as ancestral in eudicots \citep{igic_2001,steinbachs_2002}, and it is expressed in all SI species of Solanaceae examined to date.
The consequent absence of SI polyploids in this family yields a strong correlation between ploidy and breeding system \citep{robertson_2011}.
